Landscape composition and beneficial insects

### 2020-06-12 manuscript/manuscript_outline.Rmd
Found potential problem in matrix allignment within runMods

* The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover

>>>>

* Overall, we found that trees/shrubs, 
  + The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover
